---
title: 'STAT 413/613 Homework on Web Data: APIs and Scraping'
author: "Sihyuan Han"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  pdf_document:
    number_sections: yes
    toc: no
    toc_depth: '4'
urlcolor: blue

---

# Using APIs

- Pick a website of your choice (not discussed in class) that requires a free API key to download a data set. Convert elements of interest into a tibble and create a graph to answer a question of interest.
- State the question and interpret the plot.

```{r}
library(tidyverse)
library(rvest)
library(ggplot2)
```

# IMDB List of Oscar Winners

IMDB has a list of the [Oscar Best Picture Winners](https://www.imdb.com/search/title/?count=100&groups=oscar_best_picture_winners&sort=year%2Cdesc&ref_=nv_ch_osc).

Scrape the following elements, convert the data into a tibble, tidy it, and clean it to answer the questions below: 

- Number
- Title
- Year
- MPAA Rating
- Length in minutes
- Genre
- Star Rating
- Metascore Rating
- Gross Receipts

Convert the data into a tibble, tidy it, and clean it to answer the following questions:

```{r}
html_obj <- read_html("Best_Picture_ IMDb.html")
html_obj
```

```{r}
# get movie titles
oscar_titles <- html_nodes(html_obj, 
                               css = ".lister-item-header a , .text-primary")
head(oscar_titles)
titles_text <- html_text(oscar_titles)
length(titles_text)
titles_df <- tibble(text = titles_text)

titles_df %>% 
  mutate(ismovierank = str_detect(text, "^\\d+\\.$")) %>% 
  filter(ismovierank == FALSE) %>% 
  mutate(rownum = row_number()) %>% 
  select(rownum, text, -ismovierank) %>% 
  rename(rank = rownum, 
         movie = text) ->
  movie_titles
head(movie_titles)
```

```{r}
oscar_winners <- html_nodes(html_obj, 
                               css = ".ghost~ .text-muted+ span , .favorable , .ratings-imdb-rating strong , .genre , .runtime , .certificate , .unbold , .lister-item-header a")
head(oscar_winners)
ratings_text <- html_text(oscar_winners)
length(ratings_text)
```

```{r}
oscar_df <- tibble(text = ratings_text)
  oscar_df %>% 
    mutate(ismovierank = str_detect(text, "^\\d+\\.$")) -> # find sth like "1."
    oscar_df
# check how many movies are in the data
sum(datadf$ismovierank)
```

```{r}
# add cumsum
oscar_df %>% 
  mutate(movienum = cumsum(ismovierank)) ->
  oscar_df

# define movie titles
oscar_df %>% 
  mutate(isname = text %in% movie_titles$movie) ->
  oscar_df

# define years
oscar_df %>% 
  mutate(isyear = str_detect(text, "\\(\\d+\\)")) ->
  oscar_df

# define MPAA ratings (last step)

# define length in minutes
oscar_df %>% 
  mutate(islength = str_detect(text, "^\\d+\\smin$")) ->
  oscar_df

# define genre
oscar_df %>% 
  mutate(isgenre = str_detect(text, "^\\n")) ->
  oscar_df

# define star ratings
oscar_df %>% 
  mutate(isstar = str_detect(text, "^\\d\\.\\d$")) ->
  oscar_df

# define Metascore
oscar_df %>% 
  mutate(ismeta = str_detect(text, "^\\d+\\s+$")) ->
  oscar_df

# define gross
oscar_df %>% 
  mutate(isgross = str_detect(text, "^\\$\\d+\\.\\d+M$")) ->
  oscar_df

# define MPAA
oscar_df %>% 
  mutate(ismpaa = !ismovierank & !isname & !isyear & !isgenre & !islength & !isstar & !ismeta & !isgross) ->
  oscar_df
```

```{r}
# 
oscar_df %>%
  mutate(key = case_when(
    ismovierank ~ "rank",
    isname ~ "movie",
    isyear ~ "year",
    ismpaa ~ "mpaa",
    islength ~ "length",
    isgenre ~ "genre",
    isstar ~ "star_rating",
    ismeta ~ "metascore",
    isgross ~ "gross")) %>% 
  select(movienum, key, text) %>% 
  pivot_wider(names_from = key, values_from = text) ->
  oscar_movies
oscar_movies
```

```{r}
oscar_movies %>%
  mutate(rank = parse_number(rank),
         year = parse_number(year),
         length = parse_number(length),
         genre = str_replace_all(genre, "\\n", ""),
         genre = str_squish(genre),
         star_rating = parse_number(star_rating),
         metascore = parse_number(metascore),
         gross = parse_number(gross),
         movienum = NULL) ->
  oscar_movies
oscar_movies
```

1. Show a summary of the number of data elements for each movie that are not NA. Which two elements are missing the most from the movies? Metascore Rating and Gross Receipts
```{r}
oscar_movies %>% 
  is.na() %>% 
  colSums()
```

2. Create a plot of the length of a film and its gross, color coded by rating. Show linear smoothers for each rating.
- Does MPAA rating matter? Based on the plot, we can see that movies are rated as "PG-13" of MPAA rating, the longer the movies are, the gross receipts are higher
```{r}
# for star_rating
oscar_movies %>% 
  ggplot(aes(x = length, y = gross, col = star_rating)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)

# for metascore rating
oscar_movies %>% 
  ggplot(aes(x = length, y = gross, col = metascore)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)

# for MPAA rating
oscar_movies %>% 
  ggplot(aes(x = length, y = gross, col = mpaa)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)
```

3. Create a plot with a single Ordinary Least Squares smoothing line with no standard errors showing for predicting stars rating based on metacritic scores for those movies that have metacritic scores. 
- Use a linear model to assess if there is a meaningful relationship. Show the summary of the output and interpret in terms of the $p$-value and the adjusted R-Squared?
```{r}
oscar_movies %>% 
  ggplot(aes(x = metascore, y = star_rating)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)

reg.out <- lm(star_rating~metascore, data = oscar_movies)
summary(reg.out)
# p-value < 0.05, meaning there is a relationship between star and metascore ratings
# adjusted R-squared 0.08059 
```

4. Use an appropriate plot to compare the gross receipts by MPAA rating.
  + Which MPAA rating has the highest median gross receipts? 
  + Which R-rated movies are in the overall top 10 of gross receipts?
  + Use one-way analysis of variance to assess the level of evidence for whether all ratings have the same mean gross receipts. Show the summary of the results and provide your interpretation of the results.
```{r}
oscar_movies %>% 
  ggplot(aes(x = mpaa, y = gross)) +
  geom_point() +
  ggtitle("Gross Receipts vs MPAA Rating") +
  xlab("MPAA Rating") +
  ylab("Gross Receipts")

# Which MPAA rating has the highest median gross receipts? PG-13
oscar_movies %>% 
  filter(!is.na(gross)) %>% 
  group_by(mpaa) %>% 
  summarise(median_gross = median(gross)) %>% 
  arrange(desc(median_gross))

# Which R-rated movies are in the overall top 10 of gross receipts? Gladiator, Rain Man
oscar_movies %>% 
  select(movie, mpaa, gross) %>% 
  arrange(desc(gross)) %>% 
  slice(1:10) %>% 
  filter(mpaa == "R")

# ANOVA
# interpret: p-value is 0.0001579 < 0.05, so we have enough evidence to reject null hypothesis which all ratings have the same mean gross receipts. Not all means are equal (at least one pair of means is not equal)
model.fit = lm(gross~mpaa, data = oscar_movies)
anova(model.fit)
```

# Extra Credit 1 Pts

- Listen to the AI Today podcast on [Machine Learning Ops](https://podcasts.apple.com/us/podcast/ai-today-podcast-artificial-intelligence-insights-experts/id1279927057?i=1000468771571) and provide your thoughts on the following questions:  

1. Does knowing about Git and GitHub help you in understanding the podcast?  

2. How do you think the ideas of ML OPs will affect your future data science projects?  

You may also want to check out this article on [Towards Data Science](https://towardsdatascience.com/ml-ops-machine-learning-as-an-engineering-discipline-b86ca4874a3f)
